Supplementary Information

### 2020-08-27 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd

### Acknowledgements
This analysis was funded by a Smithsonian Scholarly Studies grant to KAT, SM, HCM, and CP.

>>>>

### Acknowledgements
Thanks to Pete Kerby-Miller for bark thickness data.
Helpful feedback was provided by Albert Kim...
This analysis was funded by a Smithsonian Scholarly Studies grant to KAT, SM, HCM, and CP.
